---
title: "p8105_hw6_blm2156"
author: "Britney Mazzetta"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
```

# Problem 1
```{r}
btw = read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = factor(babysex, levels = c(1,2), labels = c("male", "female")),
    frace = factor(frace, levels = c(1,2,3,4,8,9), labels = c("white", "black", "asian", "puerto rican", "other", "unknown")),
    malform = factor(malform, levels = c(0,1), labels = c("absent", "present")),
    mrace = factor(mrace, levels = c(1,2,3,4,8,9), labels = c("white", "black", "asian", "puerto rican", "other", "unknown")
  ))
btw
```
## Regression Model for Birthweight

This predictors that were selected for this regression model (baby'sex, gestational age in weeks, mother's age at delivery, mother's height, parity, mother's pre-pregnancy BMI, average number of cigarettes smoked per day during pregnancy) were selected based on literatures reviews on child's birthweight.
```{r}
reg_model1 = lm(bwt ~ babysex + gaweeks + momage + mheight + parity + ppbmi + pnumlbw + smoken, data = btw)

reg_model1
```
## Plot of model residuals against fitted values
```{r}
res_plot1 = 
btw%>%
modelr::add_residuals(reg_model1) %>%
modelr::add_predictions(reg_model1) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(color = "orange")

res_plot1
  
```
## Comparison models
Predictors for this birthweight model are length at birth and gestational age.
```{r}
comp_reg_model1 = lm(bwt ~ blength + gaweeks, data = btw)

comp_reg_model1
```
Predictors for this birthweight model are head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
comp_reg_model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = btw)

comp_reg_model2
```
Cross Validation Prediction Error
```{r, warning = FALSE}
cv_bwt = crossv_mc(btw, 100)

cv_bwt = 
  cv_bwt %>%
  mutate(reg_model1 = map(train, ~lm(bwt ~ babysex + gaweeks + momage + mheight + parity + ppbmi + pnumlbw + smoken, data = .x)),
  comp_reg_model1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
  comp_reg_model2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>%
  mutate(rmse_reg_model1 = map2_dbl(reg_model1, test, ~rmse(model = .x, data = .y)),
  rmse_comp_reg_model1 = map2_dbl(comp_reg_model1, test, ~rmse(model = .x, data = .y)),
  rmse_comp_reg_model2 = map2_dbl(comp_reg_model2, test, ~rmse(model = .x, data = .y)))

cv_bwt %>%
  select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin(color = "blue")
```

