---
title: "p8105_hw6_blm2156"
author: "Britney Mazzetta"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
```

# Problem 1

```{r}
btw = read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = factor(babysex, levels = c(1,2), labels = c("male", "female")),
    frace = factor(frace, levels = c(1,2,3,4,8,9), labels = c("white", "black", "asian", "puerto rican", "other", "unknown")),
    malform = factor(malform, levels = c(0,1), labels = c("absent", "present")),
    mrace = factor(mrace, levels = c(1,2,3,4,8,9), labels = c("white", "black", "asian", "puerto rican", "other", "unknown")
  ))
btw
```

## Regression Model for Birthweight

The predictors that were selected for this regression model (baby'sex, gestational age in weeks, mother's age at delivery, mother's height, parity, mother's pre-pregnancy BMI, average number of cigarettes smoked per day during pregnancy) were selected based on literature reviews on child's birthweight. This model was constructed based on more of a hypothesized structure for the factors that underly birthweight. 
```{r}
reg_model1 = lm(bwt ~ babysex + gaweeks + momage + mheight + parity + ppbmi + pnumlbw + smoken, data = btw)

reg_model1
```

## Plot of model residuals against fitted values

```{r}
res_plot1 = 
btw%>%
modelr::add_residuals(reg_model1) %>%
modelr::add_predictions(reg_model1) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(color = "orange")

res_plot1
  
```

## Comparison models

Predictors for this birthweight model are length at birth and gestational age.
```{r}
comp_reg_model1 = lm(bwt ~ blength + gaweeks, data = btw)

comp_reg_model1
```
Predictors for this birthweight model are head circumference, length, sex, and all interactions (including the three-way interaction) between these predictors. 
```{r}
comp_reg_model2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = btw)

comp_reg_model2
```

##Cross Validation Prediction Error

```{r, warning = FALSE}
cv_bwt = crossv_mc(btw, 100)

cv_bwt = 
  cv_bwt %>%
  mutate(reg_model1 = map(train, ~lm(bwt ~ babysex + gaweeks + momage + mheight + parity + ppbmi + pnumlbw + smoken, data = .x)),
  comp_reg_model1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
  comp_reg_model2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>%
  mutate(rmse_reg_model1 = map2_dbl(reg_model1, test, ~rmse(model = .x, data = .y)),
  rmse_comp_reg_model1 = map2_dbl(comp_reg_model1, test, ~rmse(model = .x, data = .y)),
  rmse_comp_reg_model2 = map2_dbl(comp_reg_model2, test, ~rmse(model = .x, data = .y)))

cv_bwt %>%
  select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin(color = "blue")
```

# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Bootstrap

```{r}
set.seed(3)

fcn_boots = function(df) {
  sample_frac(df, size = 0.5, replace = TRUE)
}


boot_straps = 
  tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, fcn_boots(weather_df))
  )

boot_straps
```
## Analyzing Bootstrap Samples - lnb0*b1

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>% 
  unnest(cols = c(results)) %>%
  select(strap_number, term, estimate) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>%
  janitor::clean_names() %>% 
    rename(b0 = intercept, b1 = tmin) %>%
     mutate(ln_b0b1 = log(b0*b1)) %>%
  select(-b0, -b1)


```

## Analyzing Bootstrap Samples - r^2

```{r}
bootstrap_results2 = 
  boot_straps %>%
  mutate(
    models= map(strap_sample, ~lm(tmax~tmin, data = .x)), 
    results = map(models, broom::glance)) %>%
  select(-strap_sample, -models) %>%
  unnest(cols = c(results)) %>%
  select(strap_number, r.squared)

```

## Plot of betas and r^2

```{r}
plot1 = bootstrap_results %>%
  ggplot(aes(x = ln_b0b1)) +
  geom_density(color = "purple")

plot1
```
The plot of the log of b0*b1 against density appears approximately normal. Therefore, we can infer that the 95% confidence interval is about (1.925, 2.075)


```{r}
plot2 = bootstrap_results2 %>%
  ggplot(aes(x = r.squared)) +
  geom_density(color = "purple")

plot2
```

The plot of the R2 against the density is approximately normal. Therefore, we can infer that the confidence interval is about (0.8875, 0.9375).
